---
title: "HW1 - Practice"
format: html
editor: visual
---

## Questions

∗ What do you think being a data scientist is about?

Data science can be broken down into engineering, analysis, and modeling/inference. I think most companies and modern usage of the term pertain to the engineering and analysis definitions.

∗ What differences/similarities do you see between data scientists and statisticians?

Statisticians use well-structured and clean data to do modeling and inference for the client. Data scientists are more focused on manipulating the data, but both groups use statistical analysis.

∗ How do you view yourself in relation to these two areas?

My internship the past couple of years has been focused on statistical programming, which would probably be closer to the data scientist position. I am hoping to secure a position as a statistician in the future though, so that I can do more with modeling the data and inference.

## Code Chunks

```{r}
y <- density(iris$Sepal.Length)
class(y)
typeof(y)
str(y)
```

In the code chunk above, I am creating a object y to store the density of the Sepal.Length column of the iris dataset. Then I am displaying the class, type, and structure of this new object.

Below, I am plotting the object y, the density of the Sepal.Length column, on the x-axis

```{r}
#| echo: false

plot(y)
```
